A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2022-01-07 paper/elsarticle/elsarticle-template.tex
paper

We propose a spatial AR system for wide-area metric augmentation of planar scene surfaces that produces the effect of keystone correction analytically as a function of the relative geometry of the projector and scene plane, using a projector equipped with a steerable mirror to direct the projection across varying target locations and a camera facing the scene plane in support of calibrating the system. Our system renders the placement of augmentations in the scene more intuitive than manual keystone correction in two ways. First, (i) the horizontal and vertical axes of the desired augmentations is carried out in accordance with the horizontal and vertical image axes of the camera, thereby making setting those axes as simple as appropriately rotating the camera relative to the scene plane, and thereby providing a consistent axial reference frame across all target locations. Second, (ii) the desired dimensions of the projected augmentations are specified in metric terms, thereby providing for consistent scaling, likewise across all target locations. %Our system produces such augmentations accurately, with compelling time savings relative manual keystone correction.
\end{abstract}

@@

While interest in spatial AR in industrial settings has been growing, its deployment in industrial settings remains well behind that of wearable AR systems such as handhelds or head-mounted displays. One of the main shortcomings of typical projector-based spatial AR relative to AR relying on wearables is the ability to project augmentations only within the projector's own static field of view. Here, dynamic projection systems---using steerable mirror heads to direct the projection across wider areas---has the potential to bridge the gap to wider industrial penetration. Yet the increase in the area to be covered comes with noteworthy challenges in terms of preparing the augmentations, in particular as the number of target locations in the scene becomes larger than a small handful. Considering a planar surface to be augmented (e.g., a floor, wall, or table), unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular, but will instead be subject to projective distortions (cf.\ Figure~\ref{fig:proj}). Such distortions can be corrected for by carrying out a cumbersome manual process referred to as keystone correction---involving warping an image by perturbing its corners until the desired effect is produced when projected to the scene---to appropriately warp the image to be projected, often using software bundled with the projector. Automating this manual, time-consuming, and error-prone process significantly reduces the time needed for the industrial engineering of a spatial AR application and therefore has potential to promote adoption by industry. Especially manufacturing processes of large products that remain at a static mounting position during the assembly process---i.e., industrial site assembly---offer a significant application potential for the use of spatial AR as part of worker assistance systems \cite{mayrhofer2019one}.

Our contribution is to propose a wide-area spatial AR system for planar scenes that produces the effect of keystone correction analytically, free of any manual interaction. Notably, we do this in a manner placing the $X$- and $Y$-axes of the augmentation in accordance with the $X$- and $Y$-axes of a camera placed to face downwards towards the scene plane (cf.\ Figure~\ref{fig:eval}(a)). In what follows,  \textit{we shall refer to this camera as `downwards facing'} for brevity, in quotes since the pose of the camera is likely to deviate at least gently from facing downwards to the scene plane directly (an effect for which we shall carry out a correction). Relying on the placement of the `downwards-facing' camera thus facilitates placement of augmentations, since setting the $X$- and $Y$-axes of augmentations with respect to the scene plane thus reduces to appropriately rotating the `downwards-facing' camera relative to the scene plane. We compute our corrective image warp for a given target location by warping the image to be projected using a plane-induced homography computed to produce the effect of projecting the image not from the actual projector viewpoint, but in accordance with the viewpoint of a \textit{virtual} projector (cf.\ Figure~\ref{fig:warp}). We place this virtual projector to (i) face directly downwards to the target location in the scene plane and (ii) rotate its axes to match those of the virtual camera. Moreover, our system enables specifying the dimensions of augmentations in metric terms, which we achieve by placing the virtual projector at the appropriate height above the scene plane. Finally, our system is set up for use with a projector equipped with a steerable mirror in a manner that does not call for explicitly modeling the action of the steerable mirror on the projector, thereby enabling wide-area applications exceeding the immediate field of view of the projector without needing to rely on multiple projectors.

@@

More generally, keystone correction for planar scenes can be said to reduce to computing a 2D homography \cite{Hartley2004}, an invertible transformation that preserves colinearity and is thus fittingly alternatively referred to as a `colineation'; this is the case whether computing the homography relies on manual interaction as in the case of Pinharez, or is obtained free of manual interaction as in ours. The intuition for why it is that a transformation that preserves colinearity---i.e., maps lines to lines---can serve to model an appropriate corrective image warp can be drawn from considering a planar chessboard pattern: looking at a chessboard from an oblique angle, one observes that lines parallel in the chessboard appear to meet in respective vanishing points, yet remain lines; looking at the same chessboard frontally with respect to the plane of the chessboard, lines parallel in the chessboard appear parallel in the image (i.e., they are said to meet `at infinity'). To warp an image of the chessboard acquired at one angle such that the lines of the chessboard appear as if the chessboard were acquired at another angle accordingly calls for a transformation that maps lines to lines; it therefore follows that there exists a homography that models that transformation.

One way to compute a homography is by identifying at least four correspondences between pixel positions in two images of a planar surface \cite{Hartley2004}. The keystone correction approach of Sukthankar \textit{et al.} \cite{sukthankar2001smarter} reduces to using a segmentation approach to identify the four corners of projection screen in an image acquired by a camera, and computing a homography that maps the resulting four corners of the projection screen to the four corners of the projector's image plane. Additional sensors can be used to inform the computation of a homography; Raskar and Beardsley \cite{raskar2001self} use a tilt sensor to recover the projector's gravity (i.e., down) vector, which they use to carry out a rotational correction in projecting to a wall. Still another way to compute a homography is as a function of a plane and a pair of pinhole cameras; the effect produced by the homography is one of projecting an image to the plane from the viewpoint of the one camera, and acquiring the projected image from the viewpoint of the other. Such a homography is said to be `induced' by a plane \cite{Hartley2004}. We exploit the fact that cameras and projectors alike can be modeled using a pinhole camera model \cite{bimber2019spatial}, proceed to recover the relative geometry relating the scene plane and projector, and compute a particular form of plane-induced homography to effect the intended corrective image warp, yet additionally taking into account both desired in-plane orientation and metric scale.

@@

\begin{figure}
    \centering
    \subfloat[\centering Hardware setup consisting of projector, steerable mirror system, `downwards-facing' camera (i.e., camera placed to face downards towards the scene plane, here the left view of a stereo camera).]{{\includegraphics[height=5cm]{images/system3_.pdf}}}  %3.6
    \quad
    \subfloat[\centering Measurement for augmentation, using a steel rule and a digital angle gauge (enlargements on the right).]{{\includegraphics[height=5cm]{images/meas2_.pdf}}}
    \caption{Evaluation scenario. (a) Our hardware setup, comprised of a projector, a steerable mirror system, and a stereo camera, of which we used only the left view. (b) Example augmentation produced by projecting---to one of the 15 target locations across the floorspace considered in our evaluation, to the upper-left corner of our floorspace---an image warped using our approach. The digital angle gauge reads $89.6^\circ{}$ for the top-left corner, and the steel rule 49.9 cm for the bottom edge. Corners of the full projected image extent projected to the floor in light green to provide context. Note that blur has a minimal impact on the quality of the augmentation, and hence on the accuracy of the measurements.}
    \label{fig:eval}
\end{figure}

>>>>

We propose a spatial AR system for wide-area metric augmentation of planar scene surfaces that produces the effect of keystone correction analytically as a function of the relative geometry of the projector and scene plane, using a projector equipped with a steerable mirror to direct the projection across varying target locations and a camera facing the scene plane in support of calibrating the system. Our system renders the placement of augmentations in the scene more intuitive than manual keystone correction in two ways. First, (i) the horizontal and vertical axes of the desired augmentations are set in accordance with the horizontal and vertical image axes of the camera, thereby making setting those axes as simple as appropriately rotating the camera relative to the scene plane, and thereby providing a consistent axial reference frame across all target locations. Second, (ii) the desired dimensions of the projected augmentations are specified in metric terms, thereby providing for consistent scaling, likewise across all target locations. %Our system produces such augmentations accurately, with compelling time savings relative manual keystone correction.
\end{abstract}

@@

While interest in spatial AR in industrial settings has been growing, its deployment in industrial settings lags well behind that of wearable AR systems such as handhelds or head-mounted displays. One of the main shortcomings of typical projector-based spatial AR relative to AR relying on wearables is the ability to project augmentations only within the projector's own static field of view. Here, dynamic projection systems---using steerable mirror heads to direct the projection across wider areas---have the potential to bridge the gap to wider industrial penetration. Yet the increase in the area to be covered comes with noteworthy challenges in terms of preparing the augmentations, in particular as the number of target locations in the scene becomes larger than a small handful. Considering a planar surface to be augmented (e.g., a floor, wall, or table), unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular, but will instead be subject to projective distortions (cf.\ Figure~\ref{fig:proj}). Such distortions can be corrected for by carrying out a cumbersome manual process referred to as keystone correction---involving warping an image by perturbing its corners until the desired effect is produced when projected to the scene---to appropriately warp the image to be projected, often using software bundled with the projector. Automating this manual, time-consuming, and error-prone process significantly reduces the time needed for the industrial engineering of a spatial AR application and therefore has potential to promote adoption by industry. Especially manufacturing processes of large products that remain at a static mounting position during the assembly process---i.e., industrial site assembly---offer a significant application potential for the use of spatial AR as part of worker assistance systems \cite{mayrhofer2019one}.

Our contribution is to propose a wide-area spatial AR system for planar scenes that produces the effect of keystone correction analytically, free of any manual interaction. Notably, we do this in a manner placing the $X$- and $Y$-axes of the augmentation in accordance with the $X$- and $Y$-axes of a camera placed to face downwards towards the scene plane (cf.\ Figure~\ref{fig:eval}(a)). In what follows,  \textit{we shall refer to this camera as `downwards facing'} for brevity, in quotes since the pose of the camera is likely to deviate at least gently from facing downwards towards the scene plane directly (an effect for which we shall carry out a correction). Relying on the placement of the `downwards-facing' camera thus facilitates placement of augmentations, since setting the $X$- and $Y$-axes of augmentations with respect to the scene plane thus reduces to appropriately rotating the `downwards-facing' camera relative to the scene plane. We compute our corrective image warp for a given target location by warping the image to be projected using a plane-induced homography computed to produce the effect of projecting the image not from the actual projector viewpoint, but in accordance with the viewpoint of a \textit{virtual} projector (cf.\ Figure~\ref{fig:warp}). We place this virtual projector to (i) face directly downwards to the target location in the scene plane and (ii) rotate its axes to match those of the virtual camera. Moreover, our system enables specifying the dimensions of augmentations in metric terms, which we achieve by placing the virtual projector at the appropriate height above the scene plane. Finally, our system is set up for use with a projector equipped with a steerable mirror in a manner that does not call for explicitly modeling the action of the steerable mirror on the projector, thereby enabling wide-area applications exceeding the immediate field of view of the projector without needing to rely on multiple projectors.

@@

More generally, keystone correction for planar scenes can be said to reduce to computing a 2D homography \cite{Hartley2004}, an invertible transformation that preserves colinearity and is thus fittingly alternatively referred to as a `colineation'; this is the case whether computing the homography relies on manual interaction as in the case of Pinharez, or is obtained free of manual interaction as in ours. The intuition for why it is that a transformation that preserves colinearity---i.e., maps lines to lines---can serve to model an appropriate corrective image warp can be drawn from considering a planar chessboard pattern: looking at a chessboard from one angle, one observes that lines parallel in the chessboard may appear to meet in respective vanishing points, yet always remain lines; looking at the same chessboard from another angle, one observes those same lines remain lines. Accordingly, to warp an image of the chessboard acquired at one angle such that the lines of the chessboard appear as if the chessboard were acquired at another angle accordingly calls for a transformation that maps lines to lines. Since this holds true for any set of lines in a plane, it follows that there exists a line-to-line mapping (i.e., a homography) that models the perspective transformation relating a pair of views of a plane.

One way to compute such a homography is by identifying at least four correspondences between pixel positions in two images of a planar surface \cite{Hartley2004}. The keystone correction approach of Sukthankar \textit{et al.} \cite{sukthankar2001smarter} reduces to using a segmentation approach to identify the four corners of projection screen in an image acquired by a camera, and computing a homography that maps the resulting four corners of the projection screen to the four corners of the projector's image plane. Additional sensors can be used to inform the computation of a homography; Raskar and Beardsley \cite{raskar2001self} use a tilt sensor to recover the projector's gravity vector relative to the projector, which they use to carry out a rotational correction in projecting to a wall. Still another way to compute a homography is as a function of a plane and a pair of pinhole cameras; the effect produced by the homography is one of projecting an image to the plane from the viewpoint of the one camera, and acquiring the projected image from the viewpoint of the other. Such a homography is said to be `induced' by a plane \cite{Hartley2004}. We exploit the fact that cameras and projectors alike can be modeled using a pinhole camera model \cite{bimber2019spatial}, proceed to recover the relative geometry relating the scene plane and projector, and compute a particular form of plane-induced homography to effect the intended corrective image warp, yet additionally taking into account both desired in-plane orientation and metric scale.

@@

\begin{figure}
    \centering
    \subfloat[\centering Hardware setup consisting of a Panasonic PT-RZ660BE projector, a Dynamic Projection Institute steerable mirror system, and the left view of a Stereolabs Zed 2 stereo camera to serve as the `downwards-facing' camera.]{{\includegraphics[height=5cm]{images/system3_.pdf}}}  %3.6
    \quad
    \subfloat[\centering Measurement for augmentation, using a steel rule and a digital angle gauge (enlargements on the right).]{{\includegraphics[height=5cm]{images/meas2_.pdf}}}
    \caption{Evaluation scenario. (a) Our hardware setup, comprised of a projector, a steerable mirror system, and a stereo camera, of which we used only the left view. (b) Example augmentation produced by projecting---to one of the 15 target locations across the floorspace considered in our evaluation, to the upper-left corner of our floorspace---an image warped using our approach. The digital angle gauge reads $89.6^\circ{}$ for the top-left corner, and the steel rule 49.9 cm for the bottom edge. Corners of the full projected image extent projected to the floor in light green to provide context. Note that blur has a minimal impact on the quality of the augmentation, and hence on the accuracy of the measurements.}
    \label{fig:eval}
\end{figure}
